\chapter{High-speed data transmission}

\section{Introduction}

While sensors can capture both still images and video, this project mainly concerns the latter due to its resource-intensive nature. A recent study found that 75\% of households in the United States had a high-definition television \cite{14_leichtman_research_group_2013}. The popularity of HD content makes it important to consider how bandwidth requirements increase with larger resolutions. An uncompressed 24-bit colour 1080p video at 24p has a bitrate of almost 1.2 Gbps, as calculated in Equation \ref{eq:hd_bandwidth}, well within the range where signal integrity becomes important.

\begin{equation}
  \begin{split}
    \mathbf{BW} &= (1920*1080) \, \mathrm{pixels} * 24  \, \mathrm{bpp} * 24 \, \mathrm{fps} \\
                &= 1.19  \, \mathrm{Gbps}
  \end{split}  
  \label{eq:hd_bandwidth}
\end{equation}

When transmitting a high-frequency signal between two devices, close attention must be paid to many aspects of the design to ensure that the signal integrity is preserved. The basic premise of signal integrity is covered here, however later sections will cover the issue in greater depth. With low-frequency signals, a wire or PCB trace can be modelled as an ideal circuit, without resistance, capacitance or inductance. As the frequency increases however, so-called transmission line effects are prominent and the \gls{ac} characteristics of the wire become very important. If there is a mismatch between the source, line and receiver impedances then the transmitted signal will not be fully absorbed at the load, resulting in any excess energy rebounding between source and receiver repeatedly until it has been fully absorbed. Due to superposition, the reflected waves will cause ringing and other signal integrity issues that reduce signal quality. If the issue is severe enough, the receiver cannot correctly interpret the signal and bit errors will occur. Parallel wires can also cause mutual inductance problems whereby the magnetic field generated by current travelling through one wire, will induce a current in the adjacent wire. Similarly, mutual capacitance is caused by the coupling of the two electric fields. These issues can be mitigated by taking care to ensure that impedance is properly controlled and \gls{pcb} traces are placed with care when designing circuits \cite{15_basic_principles_of_signal_integrity_2007}.

Table \ref{table:existing_protocols} shows a list of existing protocols / interfaces for transmitting image data.

\begin{table}
  \centering
  \begin{tabular}{llllll}
  Name      & Parent  & Family    & Bandwidth & Scheme  & Complexity \\
  \hline
  USB3 Vision   & USB 3   & USB       & 2.8 Gbps  & Serial  & High \\
  GigE Vision   & IP / UDP  & Ethernet    & 800 Mbps  & Serial  & Medium \\
  Camera Link   & N/A     & Camera Link   & 6.8 Gbps  & Serial  & Medium \\
  MIPI CSI-3  & M-PHY   & MIPI      & 23.2 Gbps & Serial  & Medium \\
  HDMI 2.0    & N/A     & HDMI      & 18 Gbps   & Serial  & Low / Medium
  \end{tabular}
  \caption{Existing protocols and interfaces for transmitting image data      \protect\cite{16_von_fintel_2013,17_arrowdevices.com_2014,18_hdmi.org}}.
  \label{table:existing_protocols}
\end{table}